---
title: "extra_exercises"
format: html
editor: visual
---

# About the data

These exercises use the data file `gov_env_2015.csv`. This data set includes environmental and government data on 150+ countries for 2015. The original data comes from https://www.gu.se/en/quality-government/qog-data, but variables have been renamed and some values may have been changed.

Each row in the data set is a country-year observation.

Variables:

- **country**: name of the country
- **region**: region that the country is in
- **population**
- **electoral_comp**: categorical measure of what type of elections a country has:
  1.  No elections
  2.  Single-party elections
  3.  Non-democratic multi-party elections
  4.  Democratic elections
- **globalization**: a scale of economic, political, and social globalization with a theoretical range of 1 to 100. Higher values indicate greater globalization.
- **monarchy**: binary indicator of whether a country is a monarchy (monarchy = 1)
- **presidential**: binary indicator of whether a country is a presidential system (presidential = 1)
- **democracy**: binary indicator of whether a country is a democracy (democracy = 1)
- **gdp_per_capita**: real GDP per capita in 2011 US dollars
- **rain_avg**: average annual rainfall in mm
- **temp_avg**: average annual temperature in degrees Celsius
- **climate_laws_policies**: number of climate change laws and policies enacted
- **co2_per_capita**: CO2 emissions in metric tons per capita
- **co2_growth_rate**: adjusted rate of growth in CO2 emissions
- **ag_land_pct**: % of land used for agriculture
- **forest_land_pct**: % of land that is forest
- **nat_disaster_damage**: estimated damage from natural disasters, in thousands of US dollars
- **nat_disaster_affected**: number of people affected by natural disasters
- **nat_disaster_deaths**: number of deaths from natural disasters
- **nat_disaster_n**: number of natural disasters

# Reading data

Using `read_csv` to read the "gov_env_2015.csv" data set inside the "data" folder. Save it in a variable called `govenv`. Make sure to also load any R packages you will need.

```{r}

```

# Subseting data 1

Select the columns that start with "co2".

```{r}

```

# Subseting data 2

What are the countries with higher than average `co2_per_capita`?

```{r}

```

# Subseting data 3

What is the most common region for the countries that are not democracies?

```{r}

```

# Mutating data

Replace the missing values in `climate_laws_policies` by "missing".

```{r}

```

# Summarizing

Calculate the mean and the standard deviation of all numerical columns.

```{r}

```

# Grouping

Calculate the median and the variance of `co2_per_capita` by whether the country has `climate_laws_policies` or not.

```{r}

```

# Proportions

What proportions of countries are a presidential regime?

```{r}

```

# Proportions by group

What proportion of countries with different numbers of climate laws and policies are democracies versus non-democracies?

```{r}

```
